### 2024-01-21 outputs/paper/paper.qmd
paper code 1/20

---
title: "Data Analysis of Mental Health Situation from 2014 to 2023 in Toronto"
title-block-banner: true
author: "Mary Cheng"
thanks: "Code and data are avaliable at:https://github.com/marycx/Analysis-of-Mental-Health-Situation-from-2014-to-2023-in-Toronto.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "something here"
format: pdf
toc: true
number-sections: true
---

```{r}
#| message: false
#| echo: false

#### Workspace set-up ####
install.packages("tidyverse")
install.packages("knitr")
install.packages("kableExtra")
install.packages("here")
install.packages("ggbeeswarm")
library(tidyverse) # a collection of data-related packages
library(knitr) # for kable
library(kableExtra)
library(here)
library(ggbeeswarm)
```

##

### 2024-01-21 scripts/01-download_data.R
select year 2012-2016

@@ -1,13 +1,12 @@
 ---
-Purpose: Download and clean mental health apprehension data from opendatatoronto 
-author: Mary Cheng
+title: "Download mental health apprehension dataset from opentoronto"
+author: "Mary Cheng"
 Date: 19 January 2024
 Contact: maryc.cheng@mail.utoronto.ca
 ---
 
-
 ```{r}
-# Install required packages for data download
+# Install required packages
 install.packages("tidyverse")
 install.packages("dplyr")
 install.packages("opendatatoronto")
@@ -22,7 +21,6 @@ library(opendatatoronto)
 
 ```{r}
 # Download data from opentoronto
-# get package
 package <- show_package("mental-health-apprehensions")
 	
 package
@@ -40,11 +38,12 @@ mental_health_data
 ```
 
 ```{r}
-# Save data
-write.csv(x = mental_health_data,
-          file = "inputs/data/unedited_data.csv")
+# Since I am using Posit Cloud and this csv file is huge, Posit Cloud will only include 32000 entries. Therefore, I decide to do some basic selection here regarding the years. I am going to select 2012 - 2016 to analyze.
+mental_health_data <- mental_health_data %>% filter(OCC_YEAR == "2011" | OCC_YEAR == "2012" | OCC_YEAR == "2013" | OCC_YEAR == "2014" | OCC_YEAR == "2015" | OCC_YEAR == "2016")
 ```
 
 ```{r}
-
+# Save data
+write.csv(x = mental_health_data,
+          file = "inputs/data/unedited_data.csv")
 ```

### 2024-01-21 scripts/02-clean_data.R
clean the data 1/20

@@ -1,0 +1,55 @@
+---
+purpose: "Clean the mental health apprehension dataset that was downloaded from opentoronto, and select the data that I interest."
+author: "Mary Cheng"
+Contact: maryc.cheng@mail.utoronto.ca
+date: 20 January 2023
+---
+
+```{r}
+# workspace setup; first install then load
+install.packages("tidyverse")
+install.packages("dplyr")
+install.packages("janitor")
+library(tidyverse)
+library(dplyr)
+library(janitor)
+```
+
+```{r}
+# Read in raw data
+mental_health_data = read_csv(file = "inputs/data/unedited_data.csv", show_col_types = FALSE)
+```
+
+```{r}
+# Clean data
+
+# make the names snake case
+mental_health_data_cleaned = clean_names(mental_health_data)
+
+# select the rows of interest
+mental_health_data_cleaned = 
+  mental_health_data_cleaned |>
+  select(
+    occ_year,
+    sex,
+    age_cohort,
+    premises_type
+  )
+```
+
+```{r}
+# Rename the column names so it is easy to understand
+mental_health_data_cleaned <-
+  mental_health_data_cleaned |>
+  rename(
+    occured_year = occ_year,
+    sex = sex,
+    age_group = age_cohort,
+    premises_type = premises_type
+  )
+```
+
+```{r}
+# save the cleaned csv file
+write_csv(mental_health_data_cleaned, "inputs/data/cleaned_data.csv")
+```

### 2024-01-21 scripts/01-download_data.R
download data from opentoronto

@@ -1,6 +1,6 @@
 ---
-title: "Download mental health apprehension dataset from opentoronto"
-author: "Mary Cheng"
+Purpose: Download and clean mental health apprehension data from opendatatoronto 
+author: Mary Cheng
 Date: 19 January 2024
 Contact: maryc.cheng@mail.utoronto.ca
 ---
@@ -38,12 +38,9 @@ mental_health_data
 ```
 
 ```{r}
-# Since I am using Posit Cloud and this csv file is huge, Posit Cloud will only include 32000 entries. Therefore, I decide to do some basic selection here regarding the years. I am going to select 2012 - 2016 to analyze.
-mental_health_data <- mental_health_data %>% filter(OCC_YEAR == "2011" | OCC_YEAR == "2012" | OCC_YEAR == "2013" | OCC_YEAR == "2014" | OCC_YEAR == "2015" | OCC_YEAR == "2016")
-```
-
-```{r}
 # Save data
 write.csv(x = mental_health_data,
           file = "inputs/data/unedited_data.csv")
 ```
+
+## 

### 2024-01-21 scripts/01-download_data.R
download data from opentoronto

@@ -6,13 +6,6 @@ Contact: maryc.cheng@mail.utoronto.ca
 ---
 
 ```{r}
-# Install required packages
-install.packages("tidyverse")
-install.packages("dplyr")
-install.packages("opendatatoronto")
-```
-
-```{r}
 # workspace setup
 library(tidyverse)
 library(dplyr)

### 2024-01-21 scripts/01-download_data.R
Download data from opentoronto

@@ -1,5 +1,5 @@
 ---
-Purpose: Download and clean mental health apprehension data from opendatatoronto 
+Purpose: Download mental health apprehension data from opendatatoronto 
 author: Mary Cheng
 Date: 19 January 2024
 Contact: maryc.cheng@mail.utoronto.ca
@@ -28,6 +28,11 @@ datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'
 mental_health_data <- filter(datastore_resources, row_number()==1) %>% get_resource()
 	
 mental_health_data
+```
+
+```{r}
+# Since this csv file is too huge, I can only include 32000 entries in the csv file. Therefore, I decide to do some basic selection here regarding the years. I am going to select 2012 - 2016 to analyze.
+mental_health_data <- mental_health_data %>% filter(OCC_YEAR == "2015" | OCC_YEAR == "2016" | OCC_YEAR == "2017")
 ```
 
 ```{r}

### 2024-01-21 scripts/02-clean_data.R
clean the raw data

@@ -42,7 +42,7 @@ mental_health_data_cleaned =
 mental_health_data_cleaned <-
   mental_health_data_cleaned |>
   rename(
-    occured_year = occ_year,
+    occurred_year = occ_year,
     sex = sex,
     age_group = age_cohort,
     premises_type = premises_type
@@ -53,3 +53,5 @@ mental_health_data_cleaned <-
 # save the cleaned csv file
 write_csv(mental_health_data_cleaned, "inputs/data/cleaned_data.csv")
 ```
+
+## 

### 2024-01-21 scripts/02-clean_data.R
clean raw data script

@@ -7,9 +7,6 @@ date: 20 January 2023
 
 ```{r}
 # workspace setup; first install then load
-install.packages("tidyverse")
-install.packages("dplyr")
-install.packages("janitor")
 library(tidyverse)
 library(dplyr)
 library(janitor)
@@ -47,6 +44,13 @@ mental_health_data_cleaned <-
     age_group = age_cohort,
     premises_type = premises_type
   )
+```
+
+```{r}
+# Get rid of rows with empty values, here empty values are recorded as "Not Recorded"
+mental_health_data_cleaned <- 
+  mental_health_data_cleaned %>%
+  filter(age_group != "Not Recorded" & sex != "Not Recorded" & premises_type != "Not Recorded")
 ```
 
 ```{r}

### 2024-01-21 outputs/paper/paper.qmd
update paper 1/21

@@
 ---
-title: "Data Analysis of Mental Health Situation from 2014 to 2023 in Toronto"
+title: "Data Analysis of Mental Health Situation from 2010 to 2017 in Toronto"
 title-block-banner: true
@@
 #| echo: false
-
 #### Workspace set-up ####
-install.packages("tidyverse")
-install.packages("knitr")
-install.packages("kableExtra")
-install.packages("here")
-install.packages("ggbeeswarm")
 library(tidyverse) # a collection of data-related packages
@@
 
+```{r}
+# load data
+mental_health_data = read_csv(
+  file = here("inputs/data/cleaned_data.csv"),
+  show_col_types = FALSE
+)
+```
+
+```{## Results}
+```
+
+```{r}
+# Show a piece of sample data 
+#| message: false
+#| echo: false
+#| label: tbl_sample_cleaned_data
+#| tbl_cap: Sample of cleaned mental health data
+
+mental_health_data |>
+  slice(1:10) |>
+  kable(
+    col.names = c("Occurred Year", "Sex", "Age Group", "Premises Type"),
+    digits = 1,
+    booktabs = TRUE,
+    linesep = "",
+    align = c("c", "c", "c", "c")
+  )
+
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| label: tbl-sum_occurences
+#| tbl-cap: Number of mental health apprehensions in Toronto each year from 2015-2017
+
+mental_health_data |>
+  select(occurred_year) |>
+  count(occurred_year) |>
+  kable(
+    col.names = c("Occurred Year", "Count"),
+    booktabs = TRUE,
+    align = c("c", "c")
+  )
+```
+
+```{r}
+# Analyze the relationship between mental health apprehension and gender
+#| echo: false
+#| message: false
+#| label: fig-sex_year
+#| fig-cap: Number of male and female mental health apprehensions in Toronto
+
+mental_health_data |>
+  ggplot(mapping = aes(x = occurred_year, fill = sex)) +
+  geom_bar(position = "dodge2") +
+  labs(x = "Occurred Year", y = "Number of Apprehensions", fill = "Sex") +
+  theme(legend.position = "bottom")
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| label: tbl-sum_occurences
+#| tbl-cap: Total number of mental health apprenhension in age groups in Toronto from 2015 - 0217
+
+mental_health_data |>
+  select(age_group) |>
+  count(age_group) |>
+  kable(
+    col.names = c("Age Group", "Count"),
+    booktabs = TRUE,
+    align = c("c", "c")
+  )
+```
+
+```{r}
+# Analyze the relationship between mental health apprehension and age groups in total
+#| echo: false
+#| message: false
+#| label: fig-age_year
+#| fig-cap: Total number of mental health apprenhension in age groups
+
+mental_health_data |> 
+  count(age_group) |> 
+  ggplot(mapping = aes(x = age_group, y = n)) +
+  geom_col() +
+  theme_minimal() +
+  labs(x = "Age group", y = "Number of mental health apprenhensions")
+```
+
+```{r}
+# Analyze the relationship between mental health apprehension and age groups in each year
+#| echo: false
+#| message: false
+#| label: fig-age_year_each
+#| fig-cap: Number of mental health apprenhension in age groups in each year
+
+mental_health_data |>
+  ggplot(mapping = aes(x = occurred_year, fill = age_group)) +
+  geom_bar(position = "dodge2") +
+  labs(x = "Year", y = "Number of mental health apprenhension", fill = "Age group") +
+  theme(legend.position = "bottom")
+```
+
+```{r}
+# Analyze the relationship between mental health apprehension and premises type in each year
+#| echo: false
+#| message: false
+#| label: fig-premise_type
+#| fig-cap: Percentage of mental helath apprehensions by premises type
+
+mental_health_data |>
+  count(premises_type) |>
+  ggplot(mapping = aes(x="",y = n, fill = premises_type)) +
+  geom_bar(stat = "identity", width = 1, color = "white") +
+  coord_polar(theta = "y") +
+  theme_minimal() +
+  labs(x = "", y = "Percentage of mental health apprenhension in each premises type", fill = "Age group") +
+  geom_text(aes(label = sprintf("%.1f%%", n/nrow(mental_health_data)*100)),
+            position = position_stack(vjust = 0.5), color = "white", size = 3)
+
+```
+
 ##

### 2024-01-21 scripts/01-download_data.R
download data from opentoronto

@@ -13,32 +13,17 @@ library(opendatatoronto)
 ```
 
 ```{r}
-# Download data from opentoronto
+# download the mental health act apprehension data from opentoronto
 package <- show_package("mental-health-apprehensions")
-	
-package
-	
-# get all resources for this package
+
 resources <- list_package_resources("mental-health-apprehensions")
-	
-# identify datastore resources
-datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
-	
-# load the first datastore resource as a sample
-mental_health_data <- filter(datastore_resources, row_number()==1) %>% get_resource()
-	
+
+mental_health_data <- get_resource(resource ="4a92540b-6504-4b25-827d-4511b8b9f3d9")
 mental_health_data
 ```
 
 ```{r}
-# Since this csv file is too huge, I can only include 32000 entries in the csv file. Therefore, I decide to do some basic selection here regarding the years. I am going to select 2012 - 2016 to analyze.
-mental_health_data <- mental_health_data %>% filter(OCC_YEAR == "2015" | OCC_YEAR == "2016" | OCC_YEAR == "2017")
-```
-
-```{r}
 # Save data
-write.csv(x = mental_health_data,
+write_csv(x = mental_health_data,
           file = "inputs/data/unedited_data.csv")
 ```
-
-## 

### 2024-01-21 scripts/02-clean_data.R
clean the raw data 1/21

@@ -57,5 +57,3 @@ mental_health_data_cleaned <-
 # save the cleaned csv file
 write_csv(mental_health_data_cleaned, "inputs/data/cleaned_data.csv")
 ```
-
-## 

### 2024-01-21 scripts/02-clean_data.R
cleaned the data 1/21

@@ -51,6 +51,11 @@ mental_health_data_cleaned <-
 mental_health_data_cleaned <- 
   mental_health_data_cleaned %>%
   filter(age_group != "Not Recorded" & sex != "Not Recorded" & premises_type != "Not Recorded")
+
+# Get rid of entries in 2002, 2010, 2012, and 2013, because they all have a very low number of data compared to other years, which is not helpful for my analysis.
+mental_health_data_cleaned <- 
+  mental_health_data_cleaned %>%
+  filter(occurred_year != "2002" & occurred_year != "2010" & occurred_year != "2012" & occurred_year != "2013")
 ```
 
 ```{r}

### 2024-01-23 scripts/00-simulate_data.R
simulate data

@@ -1,0 +1,32 @@
+---
+purpose: "Simulate dataset of Mental Health Act apprehension in Toronto from 2014 to 2023"
+author: "Mary Cheng"
+Contact: maryc.cheng@mail.utoronto.ca
+date: 22 January 2023
+---
+
+```{r}
+# workspace setup
+library(tidyverse)
+```
+
+```{r}
+# set seed in order to produce same output
+set.seed(63)
+```
+
+```{r}
+# Create 25 sample data entries with 4 data features (occurred_year, sex, age_group, premises_type)
+
+simulate_data <-
+  tibble(
+    occurred_year = sample(x = 2014:2023, size = 25, replace = TRUE),
+    sex = sample(x = c("male", "female"), size = 25, replace = TRUE),
+    age_group = sample(x = c("18 to 24", "25 to 34", "35 to 44", "45 to 54", "55 to 64", "65+"), size = 25, replace = TRUE),
+    premises_type = sample(x = c("Apartment", "Commercial", "Educational", "House", "Other", "Outside", "Transit"), size = 25, replace = TRUE),
+  )
+
+simulate_data
+```
+
+## 

### 2024-01-23 scripts/04-test_data.R
test data

@@ -1,0 +1,42 @@
+---
+purpose: "Test the cleaned dataset"
+author: "Mary Cheng"
+Contact: maryc.cheng@mail.utoronto.ca
+date: 22 January 2023
+---
+
+```{r}
+# Workspace set-up
+library(tidyverse)
+```
+
+```{r}
+# load data
+test_mental_health_data = read_csv(
+  file = here("inputs/data/cleaned_data.csv"),
+  show_col_types = FALSE
+)
+```
+
+```{r}
+# Start testing
+
+# Test if "sex" is exclusively one of these two: "Male" or "Female"
+test_mental_health_data$sex |>
+  unique() == c("Male", "Female")
+
+# Test if "occurred_year" is a numeric value, not a character
+test_mental_health_data$occurred_year |> class() == "numeric"
+
+# Test if "age_group" contains all 6 categories
+test_mental_health_data$age_group |>
+  unique() |>
+  length() == 6
+
+# Test if "premises_type" contains all 7 categories
+test_mental_health_data$premises_type |>
+  unique() |>
+  length() == 7
+```
+
+## 

### 2024-01-23 outputs/paper/paper.qmd
paper draft 1

--- 2024-01-21 outputs/paper/paper.qmd
@@
 ---
-title: "Data Analysis of Mental Health Situation from 2014 to 2023 in Toronto"
+title: "Data Analysis of Mental Health Trends from 2014 to 2023 in Toronto"
 title-block-banner: true
@@
 number-sections: true
+bibliography: references.bib
 ---
+
+## Introduction
+
+Mental health is an important and essential aspect of an individual's well-being.
+It plays a key role in shaping individuals' lives and decisions.
+Good mental health of the community also has a significant influence on the development and safety of society.
+In [@citesociety], it states that approximately 25% of the worldwide population is affected by mental health issues at some point in their life.
+However, a study has estimated that less than 40 percent of individuals with mental health illnesses have received consistent mental health support and treatment throughout the years in the United States[@citeMHAeffect].
+In recent years, there has been a growing recognition of the importance of mental health [@citeLiteracy]; individuals have higher mental health literacy and understanding about the importance and necessity of mental health treatment.
+
+In Ontario, Mental Health Act (MHA)[@citeMHA], which was established in 1967, provides assistance to people with mental health concerns.
+The current version is published on Dec.
+21st, 2015.
+It governs the delivery of mental health services and the protection of individuals' rights in the context of mental health care.
+It guarantees the access to care for individuals who may be at risk of harm to themselves or others due to their mental health conditions.
+All of these upsides that MHA brings strongly help the people in need: this paper[@citeMHAeffect] discusses how MHA helps creating a trend toward an increasing rate of civil commitments in taking the treatment for mental health conditions.
+
+In this paper, we use R[@citeR] to analyze a dataset from opendatatoronto[@citeODT] on the occurrences of MHA apprehension in Toronto from 2014 to 2023[@citeMentalData] in order to get a better idea on the development of mental health situation and what factors are influencing individuals' mental health.
+This report first looks at the overall trend of mental health situation across 2014 to 2023 after conducting data cleaning and pre-processing.
+It then attempts to analyze the intricate relationships between mental health conditions and demographic factors such as age, sex, and premise type, using graphs and tables.
+It is shown that the occurrences of male MHA apprehension are higher than female MHA apprehension in each year between 2014 to 2023.
+Also, from various age groups, age group "25 to 34" has the highest occurrences of MHA apprehensions compared to other age groups.
+Moreover, it is found that the number of individuals living in "Apartment" has a higher percentage of getting MHA apprehension compared to people living in other places.
+However, this is slightly biased since majority of people in Toronto lives in apartments due to the packed city.
+
+The remainder of this paper is structured as follows: Section 2 first discusses the data including data pre-processing and data overview, then presents the results, showing the relationships between mental health and demographic factors such as age, sex, and premise type.
 
@@
 #| echo: false
-
-#### Workspace set-up ####
-install.packages("tidyverse")
-install.packages("knitr")
-install.packages("kableExtra")
-install.packages("here")
-install.packages("ggbeeswarm")
+# Workspace set-up
 library(tidyverse) # a collection of data-related packages
@@
 
+```{r}
+#| message: false
+#| echo: false
+# load data
+mental_health_data = read_csv(
+  file = here("inputs/data/cleaned_data.csv"),
+  show_col_types = FALSE
+)
+```
+
+## Data
+
+The data used in this paper has been sourced from the City of Toronto's open data portal (referenced).
+Specifically, the dataset is named "Mental Health Act Apprehensions," including all Mental Health Act (MHA) Apprehensions pursuant to the Mental Health Act (Reference).
+This report incorporates information related to different gender categories, diverse age groups, and types of premises.
+The objective is to employ these data for examining the correlations among these variables and the occurrences of MHA apprehensions.
+One limitation worth noting is that each unique data entry should not be interpreted as the apprehension of a distinct individual, as an individual may be apprehended multiple times.
+However, this does not impact the analysis because the focus of the report is on the occurrences rather than the unique individuals involved.
+
+Data is pre-processed, analyzed, and explored using programming language R (REf), using \[packages...\].
+
+### Data Pre-processing
+
+Raw data downloaded from City of Toronto's open data includes 25 data features, many of which are not important in this analysis.
+Therefore, this report will not explain each of the data feature; details can be found [@citeMentalData].
+Raw dataset inlcudes 105821 data entries.
+Some data cleaning is performed.
+First, relevant data features are selected for analysis (occurred year, sex, age group, and premise types).
+Then data is cleaned by renaming the variables, so that their names are obvious.
+The variable names are as follows:
+
+1.  occurred_year: the year that the MHA apprehension occurred.
+2.  sex: sex of the person apprehende
+3.  age_group: age category of the person apprehended
+4.  premise type: the premise that the person lives in
+
+Moreover, there are certain entries containing the value "Not Recorded," which are removed to ensure the reliability and accuracy of the dataset.
+After data pre-processing, there are 104530 data entries, each with 4 features.
+A Data overview is provided in the next section to further display the data.
+
+### Data Overview
+
+This section presents an overview of the dataset following the selection of relevant variables and the cleaning process.
+
+Table @tbl_sample_cleaned_data provides some sample data entries of the refined dataset.
+It can be observed that the post-processing data comprises four columns: "Occurred Year," "Sex," "Age Group," and "Premises Type."
+
+The visualization in Figure @fig-total and Table @tbl-sum_occurences_new illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021.
+Moreover, a slight decrease is observed from 2021 to 2023.
+
+```{r}
+# Show a piece of sample data
+#| message: false
+#| echo: false
+#| label: tbl_sample_cleaned_data
+#| tbl_cap: Sample of cleaned mental health data
+
+mental_health_data |>
+  slice(1:10) |>
+  kable(
+    col.names = c("Occurred Year", "Sex", "Age Group", "Premises Type"),
+    digits = 1,
+    booktabs = TRUE,
+    linesep = "",
+    align = c("c", "c", "c", "c")
+  )
+
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| label: tbl-sum_occurences_new
+#| tbl-cap: Number of MHA apprehensions in Toronto each year from 2015-2017
+
+mental_health_data |>
+  select(occurred_year) |>
+  count(occurred_year) |>
+  kable(
+    col.names = c("Occurred Year", "Count"),
+    booktabs = TRUE,
+    align = c("c", "c")
+  )
+```
+
+```{r}
+# Total trend
+#| echo: false
+#| message: false
+#| label: fig-total
+#| fig-cap: Total number of MHA apprehensions fron 2014 to 2023
+#| 
+mental_health_data |>
+  ggplot(mapping = aes(x = occurred_year)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x = "Year", y = "Number of MHA Apprehensions") +
+  scale_x_continuous(breaks = unique(percentage$occurred_year))
+```
+
+### Relationship between Sex and Mental Health
+
+In this section, the relationship between sex and the number of MHA apprehensions will be analyzed.
+
+Table @tbl-sum_occurences_sex shows the number of male and female MHA apprehensions in Toronto from 2014 to 2023.
+It can be observed that the percentage of male MHA apprehension is generally higher than the female MHA apprehensions.
+
+Figure @fig-percentage is used to make it easier to see the trend between the year and the number of MHA apprehensions in different sex.
+As depecited in Figure @fig-percentage, it can be clearly observed that the number of male MHA apprehensions consistently surpasses that of female MHA apprehensions across the years 2014 to 2023.
+Futhermore, an observation can be made that in the year of 2020, the male MHA apprehension attained the highest number, while in the year of 2015, the female MHA apprehension attained the highest number across 2014 to 2023.
+There is also a decrease in the number of MHA apprehensions in both sexes in 2017 compared to 2015 and 2016.
+It is also worth noting that in the year of 2020, while the number of male MHA apprehensions reaches its peak, the number of female MHA apprehensions is at its lowest.
+Also, in 2015, the reverse happens: while the number of female MHA apprehensions reaches its peak, the number of male MHA apprehensions is at its lowest.
+This phenomenon is something worth analyzing in depth, and can be better understood by researching.
+
+```{r}
+#| echo: false
+#| message: false
+#| label: tbl-sum_occurences_sex
+
+# calculate the percentage of male and female MHA apprehensions in total
+percentage <- mental_health_data %>%
+  group_by(occurred_year, sex) %>%
+  summarise(count = n()) %>%
+  group_by(occurred_year) %>%
+  mutate(percentage = count / sum(count) * 100)
+
+table_output <- kable(percentage, caption = "Percentage of Male and Female MHA apprehensions from 2014 to 2023")
+table_output
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| label: fig_percentage
+
+percentage |>
+  ggplot(mapping = aes(x = occurred_year, y = percentage, color = sex)) +
+  geom_line() +
+  geom_point() +
+  labs(title = "Percentage of Male and Female Instances by Year",
+       x = "Year",
+       y = "Percentage") +
+  theme_minimal()+
+  scale_x_continuous(breaks = unique(percentage$occurred_year))
+
+```
+
+### Relationship between Age and Mental Health
+
+In this section, the relationship between age and the number of MHA apprehensions will be analyzed.
+
+Table @tbl-sum_occurences and Figure @fig-age_year displays the total occurrences of MHA apprehensions in different age groups in Toronto from 2014 to 2023.
+It can be observed that the age group "25 to 34" has the highest number of MHA apprehensions.
+Then the number of MHA apprehensions gradually decreases as the age group becomes older.
+Age group "18 to 24" and age group "35 to 44" have similar number of MHA apprehensions, which only differs by 333 occurrences.
+
+Figure @fig-age_year_each illustrates the relationship between the age group and the number of MHA apprehension in each year more clearly.
+It can be observed that the number of MHA apprehensions in age group "25 to 34" is always at the highest compared to in other age groups.
+Also, age group "65+" always has the lowest number of MHA apprehensions.
+For age group "18 to 24", "25 to 34", "35 to 44" and "45 to 54", the number of MHA apprehensions increases from 2014 to 2021, reaching its peak at 2021, and then gradually decreases from 2021 to 2023.
+For age group "65+", the number of MHA apprehensions has a consistent increasing trend from 2014 to 2023.
+
+```{r}
+#| echo: false
+#| message: false
+#| label: tbl-sum_occurences
+#| tbl-cap: Total number of MHA apprenhension in age groups in Toronto from 2014 - 2023
+
+mental_health_data |>
+  select(age_group) |>
+  count(age_group) |>
+  kable(
+    col.names = c("Age Group", "Count"),
+    booktabs = TRUE,
+    align = c("c", "c")
+  )
+```
+
+```{r}
+# Analyze the relationship between MHA apprehension and age groups in total
+#| echo: false
+#| message: false
+#| label: fig-age_year
+#| fig-cap: Total number of MHA apprenhension in age groups
+
+mental_health_data |> 
+  count(age_group) |> 
+  ggplot(mapping = aes(x = age_group, y = n)) +
+  geom_col() +
+  theme_minimal() +
+  labs(x = "Age group", y = "Number of MHA apprenhensions")
+```
+
+```{r}
+# Analyze the relationship between MHA apprehension and age groups in each year
+#| echo: false
+#| message: false
+#| label: fig-age_year_each
+#| fig-cap: Number of MHA apprenhension in age groups in each year
+
+mental_health_data |>
+  ggplot(mapping = aes(x = occurred_year, fill = age_group)) +
+  geom_bar(position = "dodge2") +
+  labs(x = "Year", y = "Number of MHA apprenhension", fill = "Age group") +
+  theme(legend.position = "bottom") +
+  scale_x_continuous(breaks = unique(percentage$occurred_year))
+```
+
+### Relationship between Premises Type and Mental Health
+
+In this section, the relationship between premises type and the number of MHA apprehensions will be analyzed.
+
+As illustrated in Figure @fig-premise_type, the distribution of the number of MHA apprehensions across various premise types is presented as percentages.
+It can be seen that "Apartment" emerges as the predominant category in premise types.
+In total, 40.9% of MHA apprehension of individuals live in "Apartment".
+MHA apprehensions of individuals living in "House" has the second largest percentage (17.8%) compared to others.
+The number of MHA apprehensions of individuals living in "Outside" and "Other" are approximately the same, which are 16.4% and 16.7% respectively.
+The remaining 8.2% includes individuals living in "Commercial", "Transit", "Educational" buildings, which do not have significant effects in the context of MHA apprehensions.
+
+```{r}
+# Analyze the relationship between MHA apprehension and premises type
+#| echo: false
+#| message: false
+#| label: fig-premise_type
+#| fig-cap: Percentage of MHA apprehensions by premises type
+
+mental_health_data |>
+  count(premises_type) |>
+  ggplot(mapping = aes(x="",y = n, fill = premises_type)) +
+  geom_bar(stat = "identity", width = 1, color = "white") +
+  coord_polar(theta = "y") +
+  theme_minimal() +
+  labs(x = "", y = "Percentage of MHA apprenhension in each premises type", fill = "Age group") +
+  geom_text(aes(label = sprintf("%.1f%%", n/nrow(mental_health_data)*100)),
+            position = position_stack(vjust = 0.5), color = "white", size = 3)
+```
+
 ##
+
+##

### 2024-01-23 outputs/paper/paper.qmd
Paper draft commit 1/22

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "something here"
+abstract: "In today's society, acknowledging the importance of mental health and the growing awareness surrounding it has increased more and more.
+This paper explores the 'Mental Health Act (MHA) Apprehension' data from opendatatoronto, the study analyzes trends in mental health situations and their correlation with those factors.
+Findings indicate there are higher MHA apprehensions among males.
+Also, the age group '25 to 34' shows the highest occurrences of MHA apprehensions.
+Additionally, individuals living in apartments are more likely to face MHA apprehension.
+The paper provides insights into the relationships among mental health conditions and age, gender, and living arrangements, offering a concise overview of the complex dynamics."
 format: pdf
 toc: true
-number-sections: true
 bibliography: references.bib
@@
 
-Mental health is an important and essential aspect of an individual's well-being.
+Mental health is an essential aspect of an individual's well-being.
 It plays a key role in shaping individuals' lives and decisions.
@@
 
-```{r}
-#| message: false
-#| echo: false
+```{r setup, include=FALSE}
+#| message: FALSE
+#| echo: FALSE
 # Workspace set-up
+knitr::opts_chunk$set(echo = FALSE)
 library(tidyverse) # a collection of data-related packages
 library(knitr) # for kable
-library(kableExtra)
 library(here)
-library(ggbeeswarm)
 ```
@@
 ```{r}
-#| message: false
-#| echo: false
+#| message: FALSE
+#| echo: FALSE
 # load data
@@
 
-Data is pre-processed, analyzed, and explored using programming language R (REf), using \[packages...\].
+Data is cleaned and analyzed using open-source statistically programming language R[@citeR], using packages from tidyverse[@citeTidyverse], dplyr[@citeDplyr], knitr[@citeKnitr], tibble[@citeTibble], and janitor[@citeJanitor].
 
@@
 
-Table @tbl_sample_cleaned_data provides some sample data entries of the refined dataset.
+@tbl-sampledata provides some sample data entries in the refined dataset.
 It can be observed that the post-processing data comprises four columns: "Occurred Year," "Sex," "Age Group," and "Premises Type."
 
-The visualization in Figure @fig-total and Table @tbl-sum_occurences_new illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021.
+The visualization in @fig-total and @tbl-sum_occurences_new illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021.
 Moreover, a slight decrease is observed from 2021 to 2023.
@@
 ```{r}
+#| echo: FALSE
+#| message: FALSE
+#| label: tbl-sampledata
+#| tbl-cap: Sample of cleaned mental health data
+
 # Show a piece of sample data
-#| message: false
-#| echo: false
-#| label: tbl_sample_cleaned_data
-#| tbl_cap: Sample of cleaned mental health data
-
 mental_health_data |>
@@
   )
-
 ```
@@
 ```{r}
-#| echo: false
-#| message: false
+#| echo: FALSE
+#| message: FALSE
 #| label: tbl-sum_occurences_new
-#| tbl-cap: Number of MHA apprehensions in Toronto each year from 2015-2017
+#| tbl-cap: Number of MHA apprehensions in Toronto each year from 2014-2023
 
+# count the sum in each year
 mental_health_data |>
@@
 ```{r}
+#| echo: FALSE
+#| message: FALSE
+#| label: fig-total
+#| fig-cap: Total number of MHA apprehensions in each year
+
 # Total trend
-#| echo: false
-#| message: false
-#| label: fig-total
-#| fig-cap: Total number of MHA apprehensions fron 2014 to 2023
-#| 
 mental_health_data |>
@@
   labs(x = "Year", y = "Number of MHA Apprehensions") +
-  scale_x_continuous(breaks = unique(percentage$occurred_year))
+  scale_x_continuous(breaks = unique(mental_health_data$occurred_year))
 ```
+
+\pagebreak
 
@@
 
-Table @tbl-sum_occurences_sex shows the number of male and female MHA apprehensions in Toronto from 2014 to 2023.
+@tbl-sum_occurences_sex shows the number of male and female MHA apprehensions in Toronto from 2014 to 2023.
 It can be observed that the percentage of male MHA apprehension is generally higher than the female MHA apprehensions.
 
-Figure @fig-percentage is used to make it easier to see the trend between the year and the number of MHA apprehensions in different sex.
-As depecited in Figure @fig-percentage, it can be clearly observed that the number of male MHA apprehensions consistently surpasses that of female MHA apprehensions across the years 2014 to 2023.
+The scatter plot @fig-percentage is used to make it easier to see the trend between the year and the number of MHA apprehensions in different sex.
+As depecited in @fig-percentage, it can be clearly observed that the number of male MHA apprehensions consistently surpasses that of female MHA apprehensions across the years 2014 to 2023.
 Futhermore, an observation can be made that in the year of 2020, the male MHA apprehension attained the highest number, while in the year of 2015, the female MHA apprehension attained the highest number across 2014 to 2023.
@@
 ```{r}
-#| echo: false
-#| message: false
+#| echo: FALSE
+#| message: FALSE
 #| label: tbl-sum_occurences_sex
+#| tbl-cap: Percentage of Male and Female MHA apprehensions in each year
 
@@
 
-table_output <- kable(percentage, caption = "Percentage of Male and Female MHA apprehensions from 2014 to 2023")
+table_output <- kable(percentage, align = c("c", "c", "c", "c"))
 table_output
@@
 ```{r}
-#| echo: false
-#| message: false
-#| label: fig_percentage
+#| echo: FALSE
+#| message: FALSE
+#| label: fig-percentage
+#| fig-cap: Percentage of male and female MHA apprehension percentage from 2014 to 2023
+# draw a scatter plot for the percentage of male and female in each year
+percentage <- mental_health_data %>%
+  group_by(occurred_year, sex) %>%
+  summarise(count = n()) %>%
+  group_by(occurred_year) %>%
+  mutate(percentage = count / sum(count) * 100)
 
@@
   geom_point() +
-  labs(title = "Percentage of Male and Female Instances by Year",
+  labs(
        x = "Year",
@@
   theme_minimal()+
-  scale_x_continuous(breaks = unique(percentage$occurred_year))
+  scale_x_continuous(breaks = unique(mental_health_data$occurred_year))
 
 ```
+
+\pagebreak
 
@@
 
-Table @tbl-sum_occurences and Figure @fig-age_year displays the total occurrences of MHA apprehensions in different age groups in Toronto from 2014 to 2023.
+@tbl-sum_occurences and @fig-age_year displays the total occurrences of MHA apprehensions in different age groups in Toronto from 2014 to 2023.
 It can be observed that the age group "25 to 34" has the highest number of MHA apprehensions.
@@
 
-Figure @fig-age_year_each illustrates the relationship between the age group and the number of MHA apprehension in each year more clearly.
+@fig-age_year_each illustrates the relationship between the age group and the number of MHA apprehension in each year more clearly.
 It can be observed that the number of MHA apprehensions in age group "25 to 34" is always at the highest compared to in other age groups.
@@
 ```{r}
-#| echo: false
-#| message: false
+#| echo: FALSE
+#| message: FALSE
 #| label: tbl-sum_occurences
@@
 ```{r}
-# Analyze the relationship between MHA apprehension and age groups in total
-#| echo: false
-#| message: false
+#| echo: FALSE
+#| message: FALSE
 #| label: fig-age_year
 #| fig-cap: Total number of MHA apprenhension in age groups
-
+# Analyze the relationship between MHA apprehension and age groups in total
 mental_health_data |> 
@@
 ```{r}
-# Analyze the relationship between MHA apprehension and age groups in each year
-#| echo: false
-#| message: false
+#| echo: FALSE
+#| message: FALSE
 #| label: fig-age_year_each
 #| fig-cap: Number of MHA apprenhension in age groups in each year
-
+# Analyze the relationship between MHA apprehension and age groups in each year
 mental_health_data |>
@@
 
+\pagebreak
+
 ### Relationship between Premises Type and Mental Health
@@
 
-As illustrated in Figure @fig-premise_type, the distribution of the number of MHA apprehensions across various premise types is presented as percentages.
+As illustrated in @fig-premise_type, the distribution of the number of MHA apprehensions across various premise types is presented as percentages.
 It can be seen that "Apartment" emerges as the predominant category in premise types.
@@
 ```{r}
-# Analyze the relationship between MHA apprehension and premises type
-#| echo: false
-#| message: false
+#| echo: FALSE
+#| message: FALSE
 #| label: fig-premise_type
@@
 
+# Analyze the relationship between MHA apprehension and premises type
 mental_health_data |>
@@
 
-##
+\pagebreak
 
-##
+## Reference

### 2024-01-23 outputs/paper/paper.qmd
finish paper 1/23

@@
 
-The visualization in @fig-total and @tbl-sum_occurences_new illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021.
+The visualization in @fig-total and @tbl-sum_occurences_new illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021 (13219 occurrences).
 Moreover, a slight decrease is observed from 2021 to 2023.
@@
 
-```{r}
+```{r out.width="65%", fig.align='center'}
 #| echo: FALSE
@@
 As depecited in @fig-percentage, it can be clearly observed that the number of male MHA apprehensions consistently surpasses that of female MHA apprehensions across the years 2014 to 2023.
-Futhermore, an observation can be made that in the year of 2020, the male MHA apprehension attained the highest number, while in the year of 2015, the female MHA apprehension attained the highest number across 2014 to 2023.
+Futhermore, an observation can be made that in the year of 2020, the male MHA apprehension attained the highest percentage (58.55%), while in the year of 2015, the female MHA apprehension attained the highest percentage (44.26%) across 2014 to 2023.
 There is also a decrease in the number of MHA apprehensions in both sexes in 2017 compared to 2015 and 2016.
-It is also worth noting that in the year of 2020, while the number of male MHA apprehensions reaches its peak, the number of female MHA apprehensions is at its lowest.
-Also, in 2015, the reverse happens: while the number of female MHA apprehensions reaches its peak, the number of male MHA apprehensions is at its lowest.
+It is also worth noting that in the year of 2020, while the number of male MHA apprehensions reaches its peak, the number of female MHA apprehensions is at its lowest (differs by 17.1%).
+Also, in 2015, the reverse happens: while the number of female MHA apprehensions reaches its peak, the number of male MHA apprehensions is at its lowest (differs by 11.48%).
 This phenomenon is something worth analyzing in depth, and can be better understood by researching.
 
-```{r}
+Overall, it can be concluded that males have a higher number of MHA apprehensions that females.
+
+```{r tbl.}
 #| echo: FALSE
@@
   group_by(occurred_year) %>%
-  mutate(percentage = count / sum(count) * 100)
+  mutate(percentage = format(round((count / sum(count) * 100),2), nsmall = 2))
 
@@
 
-```{r}
+```{r out.width="70%", fig.align='center'}
 #| echo: FALSE
@@
 # draw a scatter plot for the percentage of male and female in each year
-percentage <- mental_health_data %>%
-  group_by(occurred_year, sex) %>%
-  summarise(count = n()) %>%
-  group_by(occurred_year) %>%
-  mutate(percentage = count / sum(count) * 100)
 
@@
 @tbl-sum_occurences and @fig-age_year displays the total occurrences of MHA apprehensions in different age groups in Toronto from 2014 to 2023.
-It can be observed that the age group "25 to 34" has the highest number of MHA apprehensions.
+It can be observed that the age group "25 to 34" has the highest number of MHA apprehensions (30186 occurrences).
 Then the number of MHA apprehensions gradually decreases as the age group becomes older.
@@
 For age group "65+", the number of MHA apprehensions has a consistent increasing trend from 2014 to 2023.
+
+Overall, it can be implied that individuals in age group "25 to 34" have the highest number of MHA apprehensions compared to other age groups.
 
@@
 
+Overall, a conclusion can be reached that individuals living in "Apartment" have the highest occurrences of MHA apprehension.
+
 ```{r}

### 2024-01-23 outputs/paper/paper.qmd
finish paper 1/23

@@
 title: "Data Analysis of Mental Health Trends from 2014 to 2023 in Toronto"
-title-block-banner: true
 author: "Mary Cheng"
 thanks: "Code and data are avaliable at:https://github.com/marycx/Analysis-of-Mental-Health-Situation-from-2014-to-2023-in-Toronto.git"
-date: "`r format(Sys.time(), '%d %B %Y')`"
+date: today
+date-format: long
 abstract: "In today's society, acknowledging the importance of mental health and the growing awareness surrounding it has increased more and more.

### 2024-01-25 outputs/paper/paper.qmd
fix some typo

@@
 abstract: "In today's society, acknowledging the importance of mental health and the growing awareness surrounding it has increased more and more.
-This paper explores the 'Mental Health Act (MHA) Apprehension' data from opendatatoronto, the study analyzes trends in mental health situations and their correlation with those factors.
-Findings indicate there are higher MHA apprehensions among males.
+This paper explores the 'Mental Health Act (MHA) Apprehension' data from opendatatoronto.
+The study analyzes trends in mental health situations and their correlation with those factors.
+Findings illustrate that number of MHA apprehensions is at its highest in 2021.
+It also indicates there are higher MHA apprehensions among males.
 Also, the age group '25 to 34' shows the highest occurrences of MHA apprehensions.
 Additionally, individuals living in apartments are more likely to face MHA apprehension.
-The paper provides insights into the relationships among mental health conditions and age, gender, and living arrangements, offering a concise overview of the complex dynamics."
+The paper provides insights into the relationships among mental health conditions, age, gender, and living arrangements, offering a concise overview of the situation."
 format: pdf
@@
 Good mental health of the community also has a significant influence on the development and safety of society.
-In [@citesociety], it states that approximately 25% of the worldwide population is affected by mental health issues at some point in their life.
+[@citesociety] states that approximately 25% of the worldwide population is affected by mental health issues at some point in their life.
 However, a study has estimated that less than 40 percent of individuals with mental health illnesses have received consistent mental health support and treatment throughout the years in the United States[@citeMHAeffect].
@@
 
-In Ontario, Mental Health Act (MHA)[@citeMHA], which was established in 1967, provides assistance to people with mental health concerns.
-The current version is published on Dec.
-21st, 2015.
-It governs the delivery of mental health services and the protection of individuals' rights in the context of mental health care.
+In Ontario, Mental Health Act (MHA)[@citeMHA], which was established in 1967 (current version published in 2015), provides assistance to people with mental health concerns.
+It governs the involuntary admission and treatment of people with mental health disorders.
+It aims to provide mental health services and protect individuals' rights.
 It guarantees the access to care for individuals who may be at risk of harm to themselves or others due to their mental health conditions.
@@
 Moreover, it is found that the number of individuals living in "Apartment" has a higher percentage of getting MHA apprehension compared to people living in other places.
-However, this is slightly biased since majority of people in Toronto lives in apartments due to the packed city.
+However, this may be slightly biased since majority of people in Toronto lives in apartments due to the packed city.
 
@@
 library(here)
+library(kableExtra)
 ```
@@
 
-The data used in this paper has been sourced from the City of Toronto's open data portal (referenced).
-Specifically, the dataset is named "Mental Health Act Apprehensions," including all Mental Health Act (MHA) Apprehensions pursuant to the Mental Health Act (Reference).
+The data used in this paper has been sourced from the City of Toronto's open data portal [@citeODT].
+Specifically, the dataset is named "Mental Health Act Apprehensions," including all Mental Health Act (MHA) Apprehensions pursuant to the Mental Health Act [@citeMentalData].
 This report incorporates information related to different gender categories, diverse age groups, and types of premises.
@@
 
-Data is cleaned and analyzed using open-source statistically programming language R[@citeR], using packages from tidyverse[@citeTidyverse], dplyr[@citeDplyr], knitr[@citeKnitr], tibble[@citeTibble], and janitor[@citeJanitor].
+Data is cleaned and analyzed using open-source statistically programming language R[@citeR], using packages from tidyverse[@citeTidyverse], dplyr[@citeDplyr], knitr[@citeKnitr], kableExtra[@citeKableExtra], tibble[@citeTibble], and janitor[@citeJanitor].
 
@@
 
-Raw data downloaded from City of Toronto's open data includes 25 data features, many of which are not important in this analysis.
+Raw data downloaded from City of Toronto's open data includes 25 data features (see @tbl-raw for each data feature and its content), many of which are not important in this analysis.
 Therefore, this report will not explain each of the data feature; details can be found [@citeMentalData].
-Raw dataset inlcudes 105821 data entries.
+The raw dataset includes 105821 data entries.
 Some data cleaning is performed.
@@
 1.  occurred_year: the year that the MHA apprehension occurred.
-2.  sex: sex of the person apprehende
+2.  sex: sex of the person apprehended
 3.  age_group: age category of the person apprehended
-4.  premise type: the premise that the person lives in
+4.  premises_type: the premise that the person lives in
 
 Moreover, there are certain entries containing the value "Not Recorded," which are removed to ensure the reliability and accuracy of the dataset.
-After data pre-processing, there are 104530 data entries, each with 4 features.
+After data pre-processing, there are 104530 data entries, each with 4 features described above.
 A Data overview is provided in the next section to further display the data.
@@
 
-The visualization in @fig-total and @tbl-sum_occurences_new illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021 (13219 occurrences).
+@tbl-sum_occurences_new shows the total number of MHA apprehensions across 2014 to 2023.
+A bar plot is created to better visualize the general trend of the dataset.
+It can be seen in @fig-total which illustrates a gradual rise in the occurrences of MHA apprehensions from 2014 to 2021, peaking in 2021 (13219 occurrences).
 Moreover, a slight decrease is observed from 2021 to 2023.
+Some implications can be inferred from this trend.
+The reason why 2021 has the most cases of MHA apprehensions might be due to COVID-19 pandemic which was prevailing at that time.
+COVID-19 brought multifaceted challenges to people, for example, the economic uncertainty, lose of loved ones, prolonged social isolation, and so on.
+To some extent, these challenges all contributed to the increasing number of mental health problems.
+
+```{r}
+#| message: FALSE
+#| echo: FALSE
+# load data
+raw_data = read_csv(
+  file = here("inputs/data/unedited_data.csv"),
+  show_col_types = FALSE
+)
+```
+
+```{r}
+#| message: FALSE
+#| echo: FALSE
+#| label: tbl-raw
+#| tbl-cap: "Preview of the uncleaned MHA apprehension dataset"
+
+# preview the raw data
+raw_data[1:3, 1:8] |>
+  kable(booktabs = TRUE) |>
+  kable_styling(latex_options = c('scale_down'))
+raw_data[1:3, 9:18] |>
+  kable(booktabs = TRUE) |>
+  kable_styling(latex_options = c('scale_down'))
+raw_data[1:3, 19:25] |>
+  kable(booktabs = TRUE) |>
+  kable_styling(latex_options = c('scale_down'))
+```
 
@@
 mental_health_data |>
-  slice(1:10) |>
+  slice(1:6) |>
   kable(
@@
 
-Overall, it can be concluded that males have a higher number of MHA apprehensions that females.
+Overall, it can be concluded that males have a higher number of MHA apprehensions than females.
 
@@
 
-\pagebreak
-
 ### Relationship between Age and Mental Health
@@
 
-@tbl-sum_occurences and @fig-age_year displays the total occurrences of MHA apprehensions in different age groups in Toronto from 2014 to 2023.
+@tbl-sum_occurences displays the total occurrences of MHA apprehensions in different age groups in Toronto from 2014 to 2023.
 It can be observed that the age group "25 to 34" has the highest number of MHA apprehensions (30186 occurrences).
@@
 #| message: FALSE
-#| label: fig-age_year
-#| fig-cap: Total number of MHA apprenhension in age groups
-# Analyze the relationship between MHA apprehension and age groups in total
-mental_health_data |> 
-  count(age_group) |> 
-  ggplot(mapping = aes(x = age_group, y = n)) +
-  geom_col() +
-  theme_minimal() +
-  labs(x = "Age group", y = "Number of MHA apprenhensions")
-```
-
-```{r out.width="70%", fig.align='center'}
-#| echo: FALSE
-#| message: FALSE
 #| label: fig-age_year_each
@@
 
-### Relationship between Premises Type and Mental Health
+### Relationship between Premise Types and Mental Health
 
@@
 
-```{r}
+```{r fig.align='center'}
 #| echo: FALSE
@@
   ggplot(mapping = aes(x="",y = n, fill = premises_type)) +
-  geom_bar(stat = "identity", width = 1, color = "white") +
+  geom_bar(stat = "identity", width = 2, color = "white") +
   coord_polar(theta = "y") +
@@
 
-\pagebreak
+\newpage
 

### 2024-01-25 outputs/paper/paper.qmd
completed some references

@@
 Some data cleaning is performed.
-First, relevant data features are selected for analysis (occurred year, sex, age group, and premise types).
+First, relevant data features are selected for analysis (OCC_YEAR: occurred year, SEX: sex, AGE_COHORT: age group, and PREMISES_TYPE: premise types).
 Then data is cleaned by renaming the variables, so that their names are obvious.
@@
 After data pre-processing, there are 104530 data entries, each with 4 features described above.
-A Data overview is provided in the next section to further display the data.
+A data overview is provided in the next section to further display the data.
 
@@
 
+\pagebreak
+
 ### Relationship between Age and Mental Health
@@
 #| label: fig-premise_type
-#| fig-cap: Percentage of MHA apprehensions by premises type
+#| fig-cap: Percentage of MHA apprehensions by premise types
 

### 2024-01-25 outputs/paper/paper.qmd
fixed some typos and added one reference

@@
 It also indicates there are higher MHA apprehensions among males.
-Also, the age group '25 to 34' shows the highest occurrences of MHA apprehensions.
+The age group '25 to 34' shows the highest occurrences of MHA apprehensions.
 Additionally, individuals living in apartments are more likely to face MHA apprehension.
@@
 
-## Introduction
+## 1 Introduction
 
@@
 It is shown that the occurrences of male MHA apprehension are higher than female MHA apprehension in each year between 2014 to 2023.
-Also, from various age groups, age group "25 to 34" has the highest occurrences of MHA apprehensions compared to other age groups.
+Also, age group "25 to 34" has the highest occurrences of MHA apprehensions compared to other age groups.
 Moreover, it is found that the number of individuals living in "Apartment" has a higher percentage of getting MHA apprehension compared to people living in other places.
@@
 
-## Data
+## 2 Data
 
@@
 
-### Data Pre-processing
+### 2.1 Data Pre-processing
 
@@
 
-### Data Overview
+### 2.2 Data Overview
 
@@
 @tbl-sampledata provides some sample data entries in the refined dataset.
-It can be observed that the post-processing data comprises four columns: "Occurred Year," "Sex," "Age Group," and "Premises Type."
+It can be observed that the post-processing data comprises four columns: "Occurred Year," "Sex," "Age Group," and "Premises Type".
 
@@
 COVID-19 brought multifaceted challenges to people, for example, the economic uncertainty, lose of loved ones, prolonged social isolation, and so on.
-To some extent, these challenges all contributed to the increasing number of mental health problems.
+To some extent, these challenges all contributed to the increasing number of mental health problems [@citecovid].
 
@@
 
-### Relationship between Sex and Mental Health
+### 2.3 Relationship between Sex and Mental Health
 
@@
 
-### Relationship between Age and Mental Health
+### 2.4 Relationship between Age and Mental Health
 
@@
 It can be observed that the number of MHA apprehensions in age group "25 to 34" is always at the highest compared to in other age groups.
+This is possibly due to various societal and economic pressure for people in this age group.
 Also, age group "65+" always has the lowest number of MHA apprehensions.
@@
 
-### Relationship between Premise Types and Mental Health
+### 2.4 Relationship between Premise Types and Mental Health
 
@@
 In total, 40.9% of MHA apprehension of individuals live in "Apartment".
+This might be due to the fact that many people are renting apartments alone or still stranger.
+Therefore, they have very few people to talk to if they do not feel mentally well.
 MHA apprehensions of individuals living in "House" has the second largest percentage (17.8%) compared to others.
 The number of MHA apprehensions of individuals living in "Outside" and "Other" are approximately the same, which are 16.4% and 16.7% respectively.
-The remaining 8.2% includes individuals living in "Commercial", "Transit", "Educational" buildings, which do not have significant effects in the context of MHA apprehensions.
+The remaining 8.2% includes individuals living in "Commercial", "Transit", "Educational" buildings, which do not have significant effects in the context of mental health situation analysis.
 
@@
 
-## Reference
+## 3 Reference
